Individual heterogeneity in the functional network topography of medial prefrontal cortex

### 2019-05-24 Manuscript.Rmd
forgot the @ in two citations. oops

  However, strong conclusions about functional colocalization require consideration of individual-level heterogeneity in topographic patterns of brain activity. A recognized limitation of group averaging and meta-analysis is that the functional topography of the individual can be misaligned and blurred [@Fedorenko2012; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], exaggerating the apparent overlap across domains. This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [Lopez2019; @Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013]. An alternative approach is to focus on analyses at the individual-participant level. Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Tobyne2018]. Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019]. It is therefore possible that the previously reported overlap of DN and valuation effects can be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level. An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DN effects within mPFC and PCC in a large sample of individuals.

@@

Our findings show that the functional topography of mPFC is variable across a large pool of individuals, and that the SP algorithm is a useful tool for identifying this refined topography in a data-driven way. The ability to capture an individual's functional topography without the need of group priors is clinically relevant, as it could help us better characterize the heterogenous influences on neural function reported in disorders that significantly target mPFC, such as depression and schizophrenia [@Hiser2018]. Furthermore, it encourages interrogating where task-related activity for various domains is situated relative to an individual's mPFC organization. Our work is motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation and episodic memory functions [@Euston2012], self-referential thought and theory of mind [Mitchell2005], and multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010], among others. Delineating the precise neural mapping of these phenomena will allow us to better theorize about what common features compose their psycholological architecture.

>>>>

  However, strong conclusions about functional colocalization require consideration of individual-level heterogeneity in topographic patterns of brain activity. A recognized limitation of group averaging and meta-analysis is that the functional topography of the individual can be misaligned and blurred [@Fedorenko2012; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], exaggerating the apparent overlap across domains. This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Lopez2019; @Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013]. An alternative approach is to focus on analyses at the individual-participant level. Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Tobyne2018]. Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019]. It is therefore possible that the previously reported overlap of DN and valuation effects can be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level. An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DN effects within mPFC and PCC in a large sample of individuals.

@@

Our findings show that the functional topography of mPFC is variable across a large pool of individuals, and that the SP algorithm is a useful tool for identifying this refined topography in a data-driven way. The ability to capture an individual's functional topography without the need of group priors is clinically relevant, as it could help us better characterize the heterogenous influences on neural function reported in disorders that significantly target mPFC, such as depression and schizophrenia [@Hiser2018]. Furthermore, it encourages interrogating where task-related activity for various domains is situated relative to an individual's mPFC organization. Our work is motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation and episodic memory functions [@Euston2012], self-referential thought and theory of mind [@Mitchell2005], and multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010], among others. Delineating the precise neural mapping of these phenomena will allow us to better theorize about what common features compose their psycholological architecture.
